---
title: "Statistical Inference Project II"
author: "Xinli"
date: "May 19, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**1. Load the ToothGrowth data and perform some basic exploratory data analyses**
```{r}
library(datasets)
data(ToothGrowth)
require(graphics)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
      xlab = "dose")
```


**2. Provide a basic summary of the data.**
```{r}
summary(ToothGrowth)
table(ToothGrowth$dose, ToothGrowth$supp)
```


**3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.** 

Comparing tooth growth by supplements:
```{r}
OJ=ToothGrowth$len[ToothGrowth$supp=="OJ"]
VC=ToothGrowth$len[ToothGrowth$supp=="VC"]
t.test(OJ,VC)
```
The p-value is 0.006. The null hypothesis is not rejected. So supplement types have no effect on tooth length.


Comparing tooth growth by dose:
```{r}
t.test(len~dose, data=ToothGrowth[ToothGrowth$dose %in% c(0.5,1),])$p.value
t.test(len~dose, data=ToothGrowth[ToothGrowth$dose %in% c(0.5,2),])$p.value
t.test(len~dose, data=ToothGrowth[ToothGrowth$dose %in% c(1,2),])$p.value
```

Under Bonferroni correction, there are 3 tests. So adjuested alpha = alpha/3 = 0.0167. All the p values of t tests are less than adjuested alpha. So the null hypothesis is rejected. That is to say, the increase in dose leads to increase in tooth length.


**4. State your conclusions and the assumptions needed for your conclusions.**


Conclusions:

1. Supplement types have no effect on tooth length.

2. The increase in dose leads to increase in tooth length.


Assumptions:

1. The experiment was done randomized.

2. The samples could represent the population.

3. For t-tests, variances are assumed to be different. 